|

### 2021-03-21 appendix/appendix.Rmd
change todo and para appendix

Therefore, there are possibilities for having the law of 1/n in the direction predicted by @weingast1981political, and in a reverse direction, as in @primo2008distributive. Here, we showed the variation changing only the deadweight losses, but there are many other theoretical reasons, such as the limiting power of the upper houses [@malhotra], the XXXX, and XXXX. Most of the literature after @weingast1981political, attempted to find the empirical complements to this original formulation.

>>>>

Therefore, there are possibilities for having the law of 1/n in the direction predicted by @weingast1981political, and in a reverse direction, as in @primo2008distributive. Here, we showed the variation changing only the deadweight losses, but there are many other theoretical reasons, such as the limiting power of the upper houses [@chen_malhotra_2007], the XXXX, and XXXX. Most of the literature after @weingast1981political, attempted to find the empirical complements to this original formulation.
